Simulation of Congenital Heart Defect Corrective Surgeries Using Thin Shell Elements

### 2012-03-02 Doc/Miccai/results.tex
notes on results
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@379 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

In order to show an improvement on existing predictive simulation systems for CHD corrective surgeries, we want to demonstrate that our blood vessel model based on thin shell elements is
\begin{enumerate}
\item physically accurate,
\item converges to expected results with a low number of elements,
\item is able to simulate low-level surgical procedures universally.
\end{enumerate}
We close discussion with limitations and constraints of our simulation approach in terms of generation and dynamic remeshing of thin shell element meshes.

@@

It is important to minimize the number of shell elements to reduce computation time. This is the key factor to enable an interactive simulation system that is accepted by surgeons to simulate multiple surgical approaches in succession. The bending capabilities of thin shell elements allow to reduce their number by still representing the tubular structure of blood vessels while maintaining their physical behavior appropriately. Figure \ref{fig-convergence} shows simulation results of a strongly deformed tube represented by different numbers of thin shell elements. With only eight vertices along the circumference of the elastic tube the simulation result is comparable to a simulation result with high element count. We map a fine polygonal mesh to the coarse shell element meshes to visualize their intrinsic bending detail and therefore to get comparable results that correlates with the true shape of the simulated tube.

@@

\subsection{Limitations and Constraints}

>>>>

In order to show an improvement on existing predictive simulation systems for CHD corrective surgeries, we want to demonstrate that our blood vessel model based on thin shell elements is
\begin{enumerate}
\item physically accurate, \tomas{I suggest to use \uv{fitness for the purpose}}
\item converges to expected results with a low number of elements,
\item is able to simulate low-level surgical procedures universally.
\end{enumerate}
We close discussion with limitations and constraints of our simulation approach in terms of generation and dynamic remeshing of thin shell element meshes.

@@

It is important to minimize the number of shell elements to reduce computation time. This is the key factor to enable an interactive simulation system that is accepted by surgeons to simulate multiple surgical approaches in succession. The bending capabilities of thin shell elements allow to reduce their number and still representing the tubular structure of blood vessels while maintaining their physical behavior appropriately. Figure \ref{fig-convergence} shows simulation results of a strongly deformed tube represented by different numbers of thin shell elements. With only eight vertices along the circumference of the elastic tube the simulation result is comparable to a simulation result with high element count. We map a fine polygonal mesh to the coarse shell element meshes to visualize their intrinsic bending detail. \tomas{redundant, already in previous sentences: and therefore to get comparable results that correlates with the true shape of the simulated tube.}

@@

\subsection{Limitations and Constraints}
\tomas{rename do \uv{Discussion}}

More general problems for this kind of simulation: (not limited to our method)

-- getting image data -- that is something you're already working on in Germany

-- hi-quality mesh with low number of polygons -- there seem to be something already, e.g. \cite{Comas2010c}.

At the moment biggest limitation of our method resides in the requirement of the same number of nodes on both edges of the suture.
Meeting this requirement may not be easy.
Also FE methods put constrain on the quality of mesh that is necessary to maintain the convergence and stability of the model.
These are especially important for meshes with low number of elements.
To deal with this problems techniques for dynamic remeshig during the simulation may be required.
